Quality Definitions of Qualities

### 2020-02-01 StateOfPractice/QDefOfQualities/QDefOfQualities.tex

Combined definitions \ref{Installability_Selected2} and
\ref{Installability_Selected1} rephrased.  Installability refers to the
effort required for the installation, uninstallation or reinstallation of a
software or product in a specified environment.

@@

 The definition captures a vital metric of measure for this quality - effort, and considers not just the installation but uninstallation and re-installation which are all related to installation activities.  \oo{Done installability}

@@

\begin{defn}
  The ability of a system to perform its required functions under stated
  conditions whenever required—having a long mean time between failures
  \citep{mcconnell2004code}.
\end{defn}
\begin{defn} \label{reliabilitySelected2} Reliability can be estimated as ``the
  average time interval between two failures, also called the mean time to
  failure (MTTF). Clearly, MTTF (t) = 1/FI (t)''. Where FI (t) is the failure
  intensity - the number of failures per unit time \citep{GhezziEtAl2003}.
\end{defn}
\oo{Statistical definition from  \citep{GhezziEtAl2003} added}

>>>>

Combined definitions \ref{Installability_Selected2} and
\ref{Installability_Selected1} rephrased:
 Installability refers to the
effort required for the installation, uninstallation or reinstallation of a
software or product in a specified environment.

@@

 The definition captures a vital metric of measure for this quality - 
 effort, and considers not just the installation but uninstallation
 and re-installation which are all related to installation activities.

@@

\begin{defn}
  The ability of a system to perform its required functions under stated
  conditions whenever required—having a long mean time between failures
  \citep{mcconnell2004code}.
\end{defn}
\begin{defn} \label{reliabilitySelected2} Reliability is concerned with measuring
	the probability of occurence of faliure - that is, the probability of the
	observable effects of errors \citep{GhezziEtAl2003}.
\end{defn}
\oo{Statistical definition from  \citep{GhezziEtAl2003} added}
